Optimizing Structural Properties Of Neural Networks With Genetic Algorithms

### 2015-08-07 paper/paper.tex
small changes

Our concrete goal for this article was to examine which choice of genotype
parameters are optimal for learning sinusoidal waves with relatively high
or low frequencies. 
Based on preliminary simulation results we chose
$\nu\in[]$ as frequency range for the challenge $C\ix{high}$, producing
high frequency waves, and $\nu\in[]$ for $C\ix{low}$, producing low
frequency waves. 
Optimizing the fitness functions $F_{C\ix{high}}$ or $F_{C\ix{low}}$ thus
results in genotypes with the desired frequency properties.

@@

A measure that is time-shift independent and maximized for functions of
identical shape, on the contrary, is the maximum of the cross correlation 
\begin{align}
    f\ix{cor}(z, z') = \max_t \frac{\left<z, z'(\cdot
    - t)\right>}{\sqrt{\left< z, z\right> \left<z', z' \right>}}~.
\end{align}
Algorithmically, the signals $z$ and $z'$ are split into overlapping chunks
which are correlated separately.  This saves computational power and
prevents minute differences in frequency to accumulate into a huge phase
shift, so the phase only has to remain relatively constant over the
timescale of a single chunk (which is about 10 seconds of simulated time).
%This measure becomes problematic for functions that are very close to zero
%for a longer time (order of chunk size), but since we are going to work
%with superpositions of sinusoidals, this drawback
%is unproblematic.

>>>>

Our concrete goal for this article was to examine which choices of genotype
parameters are optimal for learning sinusoidal waves with relatively high
or low frequencies. 
Based on preliminary simulation results we chose
$\nu\in[0.3, 3]$ as frequency range for the challenge $C\ix{high}$, producing
high frequency waves, and $\nu\in[0.004, 0.04]$ for $C\ix{low}$, producing low
frequency waves. 
Optimizing the fitness functions $F_{C\ix{high}}$ or $F_{C\ix{low}}$ thus
results in genotypes with the desired frequency properties.

@@

A measure that is time-shift independent and maximized for functions of
identical shape is the maximum of the cross correlation 
\begin{align}
    f\ix{cor}(z, z') = \max_t \frac{\left<z, z'(\cdot
    - t)\right>}{\sqrt{\left< z, z\right> \left<z', z' \right>}}~.
\end{align}
Algorithmically, the signals $z$ and $z'$ are split into overlapping chunks
which are correlated separately.  This saves computational power and
prevents minute differences in frequency to accumulate into a huge phase
shift, so the phase only has to remain relatively constant over the
timescale of a single chunk (which is about 10 seconds of simulated time).
%This measure becomes problematic for functions that are very close to zero
%for a longer time (order of chunk size), but since we are going to work
%with superpositions of sinusoidals, this drawback
%is unproblematic.
